The Exoplanet Orbit Database \textsc{II}: Updates to exoplanets.org

### 2014-07-22 draft/ms.tex
Including secondary plot
Jason's revision of the draft with first round of comments incorporated.

% definition of symbols
\def\beq{\begin{equation}}
\def\eeq{\end{equation}}
\def\ergcms{erg~cm$^{-2}$~s$^{-1}$}
\def\ergs{erg~s$^{-1}$}
\def\mps{m~s$^{-1}$}
\def\msun{M_{\odot}}
\def\lsun{L_{\odot}}
\def\etal{~et~al.~}
\def\degree{^{\circ}}
\def\leq{\leqslant}
\def\geq{\geqslant}
\def\micron{$\mu$m}
\def\percm2{{\rm cm^{-2}}}
\def\peryr{yr$^{-1}$}
\def\kepler{\textit{Kepler}}
\def\spitzer{\textit{Spitzer}}
\def\micron{$\mu$m}
\def\mjup{$M_{\rm Jup}$}
\def\rearth{R_\oplus}
\def\mearth{M_\oplus}

@@

\title{The Exoplanet Orbit Database \textsc{II}: updates for 2014}

% leading authors
\author{Eunkyu Han\altaffilmark{1,2}}
\author{Sharon X. Wang\altaffilmark{1,2,3}}
\author{Jason T. Wright\altaffilmark{1,2,3}}
\author{Ying Feng\altaffilmark{1,2}}
\author{Ming Zhao\altaffilmark{1,2}}
\author{and Friends}

\altaffiltext{1}{Department of Astronomy \& Astrophysics, 525 Davey
  Lab, The Pennsylvania State University, University Park, PA 16802, USA;
  Send correspondence to jtwright@astro.psu.edu.}
\altaffiltext{2}{Center for Exoplanets and Habitable Worlds, The
  Pennsylvania State University, University Park, PA 16802, USA}
\altaffiltext{3}{Penn State Astrobiology Research Center, The
  Pennsylvania State University, University Park, PA 16802, USA}

@@

The Exoplanet Orbit Database (EOD) compiles orbital, transit, host star, and other
parameters of robustly dected exoplanets reported in the peer-reviewed
literature. The EOD can be navigated through the Exoplanet Data
Explorer (EDE) Plotter and Table, available on the world wide web at exoplanets.org. The EOD contains data for 1490 confirmed exoplanets as of March 2014.  
The EOD drives from the Catalog of Nearby Exoplanets \citep{Butler2006}, and the first complete documentation for the EOD and the EDE was presented in 
\cite{Wright2011}. Since then, we have expanded the scope of the
EOD to include secondary eclipse parameters, asymmetric uncertainties and etc. The EOD also incorporats the sample of over 3000 \kepler\ Objects of
Interest (KOIs) and other real planets without good orbital parameters such as those detected by microlensing and imaging. Users can download the latest version of the in tire EOD as a
single comma separated value file from the front page of exoplanets.org.

@@

% Recent development in exoplanet discoveries
Since the launch of NASA's \kepler\ mission \citep{Borucki2010}, the
number of confirmed exoplanets has increased from about 300 to over
1490 as of March 2014. \kepler\ contributed to a vast
majority of these new discoveries ($> 800$) while providing an
additional sample of over 3000 exoplanet candidates (\kepler\ Objects
of Interest, KOIs; e.g.~\citealt{Batalha2013}). The transit method has thus surpassed the radial velocity (RV) method to become the most fruitful
means of detecting exoplanets. Meanwhile, great promise lies within
the new and future exoplanet surveys and instruments with direct
imaging (e.g., the Gemini Planet Imager, GPI,
\citealt{Macintosh2014}) and microlensing (e.g., the Wide-Field
InfraRed Survey Telescope, WFIRST, \citealt{Green2012}), while the
fronts of RV and transit exoplanet searches keep expanding (e.g., the
MINiature Exoplanet RV Array, MINERVA, \citealt{Wright2014}; Habitable-zone Planet Finder, HPF, \cite{Mahadevan2012} and the
Transiting Exoplanet Survey Satellit, TESS, \citealt{Ricker2010}).

% The business of tracking planet discoveries and EOD
This paper describes our continuing efforts since \cite{Butler2006}
and \cite{Wright2011} to maintain the Exoplanet Orbit Database\footnote{See http://expoplanets.org}(EOD)
and the Exoplanets Data Explorer (EDE), to keep track of the exoplanet
discoveries, and to catalog their orbital parameters and host star
properties. There are also other entities devoted to similar efforts,
including the Extrasolar Planets Encyclopaedia\footnote{See
  \url{http://exoplanet.eu}.}  \citep{Schneider2011} and the NASA
Exoplanet Archive\footnote{See
  \url{http://exoplanetarchive.ipac.caltech.edu}.}
\citep{Akeson2013}. As described in \cite{Wright2011}, the EOD is
dedicated to cataloging properties of all \emph{robustly-detected} exoplanets with
\emph{well-determined} orbital parameters published in
\emph{peer-reviewed} literature.

% data access and popularity
The EOD is hosted at exoplanets.org, which also hosts the EDE, an
interactive table with plotting tools for all the EOD exoplanets
as well as confirmed exoplanets, without good orbital parameters and KOIs. The plottable
dataset of exoplanets.org is available for download as a single comma separated value file from the Website front page.\footnote{At
  \url{htt://exoplanets.org/csv-files/exoplanets.csv}.} The EOD is widely
used in exoplanet research (e.g., \citealt{Dawson2013},
\citealt{Howard2013}, \citealt{Kipping2013}, \citealt{Kane2014},
\citealt{Weiss2014}), and the website exoplanets.org is among the most
visited exoplanet databases, with over $47,000$ visits in 2013\footnote{Measured as "visits" by Google Analytics}.

% updates on EOD and the website
Since the documentation described in \cite{Wright2011}, the EOD has expanded its scope: we now do
not require the host star of an exoplanet to be a normal star (e.g.,
exoplanets around pulsars are now included). It now ingestes more
parameters describing the exoplanet systems and their host stars, and some
parameters have been revised or deleted. We describe our updates to the
EOD in Section~\ref{sec:update}. The EDE at exoplanets.org has also
expanded its scope and now includes the \kepler\ exoplanet candidates
(KOIs). We describe these changes in Section~\ref{sec:kepler}. The
website exoplanets.org has gone through major back-end changes since
\cite{Wright2011}, which are described in Section~\ref{sec:website}. We
summarize the updates and possible future improvements in
Section~\ref{sec:summary}.

@@

The scope of the EOD has expanded, and there are three major changes
from what was described in \cite{Wright2011}. Previously, we only
included exoplanets orbiting the ``normal stars", but now we are not
limiting the type of host stars (e.g. we included exoplanets orbiting
neutron stars). Furthermore, in \cite{Wright2011}, we only included
exoplanets that were discovered by the RV and transit methods in the
EOD, but now we also included planets discovered via timing including pulsar planets and those discovered by eclipse timing. In the
future, exoplanets discovered by any other methods with robust
detections and good orbital parameters will also be included in the
EOD including astrometric planets such as beta Pic b. Previously, we required the planets have minimum mass (m$\sin{i}$) smaller than 24\mjup, but now we require the measured mass ratio to be smaller than 24
\mjup$/\msun$ ($< 0.023)$.

The rest of the selection criteria for the EOD remain unchanged. We
still require the planets to have robust detections and well-determined
orbits (though these are not strictly quantitative and sometimes subjective; see Section~2 of
\citealt{Wright2011}). If new evidence comes to light and we are no
longer confident about the planet, we may remove it from EOD, even if the new evidence is not peer reviewed.

The purpose of the EOD has not changed: we aim to provide the readers
with a comprehensive, reliable, and up-to-date database of exoplanets
with good orbital parameters and host star properties. We do not
report \textit{all} the announced exoplanets as we are not trying to
provide ``an encyclopedic presentation of every claimed detection of an
exoplanet" \citep{Wright2011}.

@@

{\bf DISCMETH} field previously reported the method of discovery,
which was either radial velocity or transit. We have replaced DISCMETH
with {\bf PLANETDISCMETH} and \mbox{{\bf STARDISCMETH}} to better
report how exoplanet systems and individual exoplanets are first
discovered. PLANETDISCMETH reports the discovery method for the
planet, wihle STARDISCMETH reports the discovery method for the first
discovered planet around the host star. These fields are stored
in string format and have one of the following values: "RV",
"Transit", "Imaging", "Microlensing", "Timing", or "Astrometry" (no planets have "astrometry" yet).

@@

{\bf KEPID} stands for KEPler ID, which is the integer number assigned
for a Kepler host star. KEPID is only available for unconfirmed
KOI's imported directly from the Exoplanet Archive by the exoplanet.org backend. Therefore,
none of the EOD planets including confirmed Kepler planets has a KEPID, yet.

{\bf KOI} stands for Kepler Objects of Interest, which is an object
with transit signals detected by \kepler\ but have not been validated to be due to exoplanets. The KOI field defined by the \kepler\ team and showed on the Exoplanet Archive, contains a floating point
number that consists of a whole number designated to the host star
followed by a decimal number denoting a candidate planet. For example,
KOI 102 is a star suspected to host two exoplanets, and KOI 102.01 is
the inner planet candidate and KOI 102.02 is the outer one. Once a
candidate is confirmed, the NAME field of the planet is replaced by
the official \kepler\ ID (``Kepler" followed by a hyphen, an integer
and an lower case letter). The KOI number is then used as
OTHERNAME. For more information, see
Section~\ref{sec:kepler}.

{\bf EOD} is a boolean which indicates whether an exoplanet is included
in the EOD for having well-characterized orbital
parameters, such as the orbital period (PER). We added this field because exoplanets.org
now also includes robustly discovered planets that do not have
well-characterized orbits, and also \kepler\ planet candidates (see
Section~\ref{sec:kepler} for more details).

{\bf MICROLENSING, IMAGING, TIMING and ASTROMETRY} are flags which
indicate that a planet detected via theses method. For example,
MICROLENSING $=$ 1 means the planet is detected in a microlensing
event. Note that planets may be detected with multiple methods.

%------------------------------------------------------------------------------
\subsection{Orbital Parameters (e.g. RV and Transit)}\label{sec:orbit}

@@

{\bf MASS} is the mass of the planet in the unit of Jupiter
mass. Previously, we only reported the minimum mass, ($m\sin{i}$,
MSINI) of the planets. We now report the mass as well when it is
available. For example, if a planet is discovered by microlensing, we
report the actual mass of the planet according to the literature. If a
planet has both radial velocity and transit measurements, we calculate
the mass from the minimum mass $m\sin{i}$ and the orbital inclination
$i$. For convenience of plotting RV and other planets on a common mass scale (see Section~\ref{sec:kepler}, MASS is set to MSINI if the orbital inclination is not known and
the reference for MASS, MASSREF is set to ``Set to MSINI; I unknown''.

Also for plotting convenience, for KOIs without $m\sin{i}$ measured, we estimate their mass using the
mass-radius relation from the literature. For KOIs with $R<4\rearth$, we follow $M_{p}/\mearth=2.69(R_{p}/\rearth)$
from \cite{Weiss2014}; for $4\rearth<R<6\rearth$, we follow $M_{p}/\mearth=(R_{p}/\rearth)^2.06$ from
\cite{Lissauer2011}; and for $6\rearth<R<11.7\rearth$ we follow $M_{p}/\mearth=1756.7*10^{(-1.646*(11.684/(R_{p}/\rearth)-1)^{(1/2.489)})}$
from \cite{Mordasini2012}.

{\bf SEP} is a separation between the host star
and the planet in units of AU. For directly imaged planets, the
literature usually reports the projected separation and we report the
value accordingly.  If SEP is not directly measured but the semi-major
axis ($a$, A) is available, then we set SEP to A with its reference,
SEPREF, set to ``Set to A''.

{\bf I} is the orbital inclination. Previously, only transiting
systems have I measured, but now some non-transiting systems
have I's reported too. For example, one microlensing system,
OGLE-2006-BLG-109L, has I measured \citep{Bennett2010}. Also, one imaging system, $\beta$ Pic, has I measured \citep{Lagrange2009}

{\bf BIGOM} is the longitude of the ascending node ($\Omega$) in units of degrees. At the moment, no planets have this quantity measured, but astrometric orbits (e.g. from GPI) will reveal it.

{\bf LAMBDA} is the projected spin-orbit misalignment ($\lambda$) in
the plane of the sky in units of degrees. At the moment, $\lambda$
values are only available for the transiting systems, which are
measured by either the Rossiter-McLaughlin effect
\citep[e.g.,][]{Winn2005} or planet transiting star spots
\citep[e.g.,][]{Sanchis-Ojeda2012}. $\lambda$ is used because
the true spin-orbit angle, defined as the angle between the
stellar spin axis and the orbital axis, is normally not directly
measurable. We follow \cite{Fabrycky2009} where the coordinates are defined as follows: the
$z$-axis points toward the observer, the $x$-axis points along the
intersection of the sky plane and the planet's orbital plane with the
ascending node of the planet having $x<0$, and the $y$-axis completes
a right handed-triad. $\lambda$ is measured clockwise on the sky from
the $y$-axis to the projected stellar rotational axis. $\lambda$ is
not a newly added field to the EOD but we describe it here because we did not
previously report it consistently, since some literature report the ``projected
spin-orbit misalignment" as $\beta = -\lambda$ instead\footnote{In some cases, e.g. \cite{Moutou2011}, other conventions entirely appear to be used.}. We have sorted
these cases out and made sure that our $\lambda$'s are following the
definition of \cite{Fabrycky2009}.

{\bf MASSREF} and {\bf MASSURL} fields were used to report the
reference and the URL of stellar mass but now they are used for planet
mass.

@@

We report the transit parameters, which are available only when the
planet has TRANSIT Boolean equal to true. We describe two added fields since
\cite{Wright2011} below, which are used for KOI's incorporated from the Exoplanet Archive.

@@

We have added an entirely new set of fields for secondary
eclipse depths. Previously, due to the limits of instrumentation and limited
sample of exoplanets, there was not much secondary eclipse depth data
available. Since \cite{Wright2011}, as many different surveys have
been launched, more and more secondary eclipse depths at multiple
bands have become available for more and more planets. Therefore, we added
this entire new set of fields. ZZZ Refer to Ming's SE plot.

The {\bf SE} Boolean indicates whether the system has detected secondary
eclipse in any of the two Micron All-Sky Survey (2MASS;
\citealt{Skrutskie2006}) $J$, $H$, and $K_s$, Kepler photometry band,
and 4 Spitzer IRAC bands. Truth indicates the
system has at least one secondary eclipse measurement in the EOD.

@@

{\bf SET} is the epoch of secondary eclipse center, normally given in HJD but (as with other fields) when the literature reports HJD or UTC JD, we do not attempt a conversion to BJD.

@@

{\bf GAMMA} ($\gamma$) is the radial velocity of the center of mass of
the planetary system with respect to the barycentric frame and is reported in km/s.

@@

We provide the brightness of the host star measured in different
filters. We report optical magnitude and color ($V$ and $B-V$),
2MASS $J$, $H$, and $K_s$ magnitudes and, we have added {\bf KP}. Notes that the definitions of V and B in the literature vary, and are often Hipparcos values
(the stellar magnitude measured through the \kepler\ bandpass).

@@

We report the coordinates of the host star as well as the host star's
ID as designated by different catalogs.  We added the {\bf DIST} field since
\cite{Wright2011}, which is the distance to the host star in the unit
of pc. If only parallax (PAR) is given, we calculate DIST based on PAR
and vice versa. If the literature does not report DIST or PAR, then we
obtain PAR from the Hipparcos dataset by \cite{van Leeuwen2009} for stars with Hipparcos numbers. We
naively propagate the error in PAR to DIST and vice versa.

@@

We have changed the way of reporting uncertainties, especially
asymmetric ones since \cite{Wright2011}. We now report
uncertainties for a certain field X as XUPPER, XLOWER and UX. XUPPER
and XLOWER store the upper and lower 1$\sigma$ uncertainties, and they
are different when the error bars are asymmetric. UX contains the
1$\sigma$ uncertainty, and it equals $({\rm XUPPER+XLOWER})/2$ in
the case of asymmetric error bars. Fields that have XUPPER, XLOWER and
UX are: all the orbital parameters, all the transit parameters, all the
secondary eclipse fields, and all the stellar
properties and DIST and PAR.

>>>>

% definition of symbols
\def\beq{\begin{equation}}
\def\eeq{\end{equation}}
\def\ergcms{erg~cm$^{-2}$~s$^{-1}$}
\def\ergs{erg~s$^{-1}$}
\def\mps{m~s$^{-1}$}
\def\msun{M_{\odot}}
\def\lsun{L_{\odot}}
\def\etal{~et~al.~}
\def\degree{^{\circ}}
\def\leq{\leqslant}
\def\geq{\geqslant}
\def\micron{$\mu$m}
\def\percm2{{\rm cm^{-2}}}
\def\peryr{yr$^{-1}$}
\def\kepler{\textit{Kepler}}
\def\spitzer{\textit{Spitzer}}
\def\micron{$\mu$m}
\def\mjup{$M_{\rm Jup}$}
\def\rjup{$R_{\rm Jup}$}
\def\rearth{R_\oplus}
\def\mearth{M_\oplus}

@@

\title{The Exoplanet Orbit Database \textsc{II}: Updates to
  exoplanets.org}

% leading authors
\author{Eunkyu Han\altaffilmark{1,2}}
\author{Sharon X.\ Wang\altaffilmark{1,2,3}}
\author{Jason T.\ Wright\altaffilmark{1,2,3}}
\author{Y.\ Katherina Feng\altaffilmark{1,2}}
\author{Ming Zhao\altaffilmark{1,2}}
\author{Onsi Fakhouri\altaffilmark{4}}
\author{Jacob I.\ Brown\altaffilmark{1,2}}
\author{Colin Hancock\altaffilmark{1,2}}

\altaffiltext{1}{Department of Astronomy \& Astrophysics, 525 Davey
  Lab, The Pennsylvania State University, University Park, PA 16802, USA;
  Send correspondence to jtwright@astro.psu.edu.}
\altaffiltext{2}{Center for Exoplanets and Habitable Worlds, The
  Pennsylvania State University, University Park, PA 16802, USA}
\altaffiltext{3}{Penn State Astrobiology Research Center, The
  Pennsylvania State University, University Park, PA 16802, USA} 
\altaffiltext{4}{Pivotal Labs, Cloud Foundry, 875 Howard St., Fourth
  Floor, San Francisco, CA 94103}

@@

The Exoplanet Orbit Database (EOD) compiles orbital, transit, host star, and other
parameters of robustly detected exoplanets reported in the peer-reviewed
literature. The EOD can be navigated through the Exoplanet Data
Explorer (EDE) Plotter and Table, available on the World Wide Web at exoplanets.org. The EOD contains data for 1490 confirmed exoplanets as of March 2014.  
The EOD descends from a table in \citet{Butler2002} and the Catalog of Nearby Exoplanets \citep{Butler2006}, and the first complete documentation for the EOD and the EDE was presented in 
\cite{Wright2011}. In this work, we describe our work since then.  We have expanded the scope of the
EOD to include secondary eclipse parameters, asymmetric uncertainties,
and expanded the EDE to include
the sample of over 3000 \kepler\ Objects of Interest (KOIs), and other
real planets without good orbital parameters (such as many of those
those detected by microlensing and imaging.) Users can download the
latest version of the entire EOD as a single comma separated value
file from the front page of exoplanets.org.

@@

% Recent development in exoplanet discoveries
Since the launch of NASA's \kepler\ mission \citep{Borucki2010}, the
number of confirmed exoplanets has increased from about 300 to over
1490 as of March 2014. \kepler\ contributed to a majority of these new discoveries ($> 800$) while providing an
additional sample of over 4,000 exoplanet candidates (\kepler\ Objects
of Interest, KOIs; e.g.~\citealt{Batalha2013}). The transit method has thus surpassed the radial velocity (RV) method to become the most fruitful
means of detecting exoplanets. Meanwhile, great promise lies within
the new and future exoplanet surveys and instruments with direct
imaging (e.g., the Gemini Planet Imager, GPI,
\citealt{Macintosh2014}) and microlensing (e.g., the Wide-Field
InfraRed Survey Telescope, WFIRST, \citealt{Green2012}), while the
fronts of RV and transit exoplanet searches keep expanding (e.g., the
MINiature Exoplanet Radial Velocity Array, MINERVA,
\citep{Wright2014}; the Habitable-zone Planet Finder, HPF, \cite{Mahadevan2012} and the
Transiting Exoplanet Survey Satellit, TESS, \citealt{Ricker2014}).

% The business of tracking planet discoveries and EOD
This paper describes our continuing efforts since \cite{Butler2006}
and \cite{Wright2011} to maintain the Exoplanet Orbit Database\footnote{See \url{http://expoplanets.org}}(EOD)
and the Exoplanets Data Explorer (EDE), to keep track of exoplanet
discoveries, and to better catalog orbital parameters and host star
properties.

There are other entities devoted to similar efforts,
including the Extrasolar Planets Encyclopaedia\footnote{See
  \url{http://exoplanet.eu}.}  \citep{Schneider2011} and the NASA
Exoplanet Archive\footnote{See
  \url{http://exoplanetarchive.ipac.caltech.edu}.}
\citep{Akeson2013}.  The natures of these efforts are complementary, and to the
degree that they are redundant provide important cross-checking and
validation.  As described in \cite{Wright2011}, the EOD is
dedicated to cataloging properties of all \emph{robustly-detected} exoplanets with
\emph{well-determined} orbital parameters published in
\emph{peer-reviewed} literature, and providing outstanding data
exploration and visualization tools for these planets.

% data access and popularity
The EOD is hosted at the Web domain exoplanets.org, which also hosts the EDE, an
interactive table with plotting tools for all the EOD exoplanets, in
addition to other confirmed exoplanets without good orbital
parameters, and KOIs (except for those with a ``FALSE POSITIVE''
disposition at the Exoplanet Archive). The entire dataset of exoplanets.org is available for download as a single comma separated value file from the Website front page.\footnote{At
  \url{http://exoplanets.org/csv-files/exoplanets.csv}.}  An example
of this CSV file is available with the electronic version of this paper.

The EOD is widely
used in exoplanet research (e.g., \citealt{Dawson2013},
\citealt{Howard2013}, \citealt{Kipping2013}, \citealt{Kane2014},
\citealt{Weiss2014}), and the website exoplanets.org had over $47,000$ visits in
2013\footnote{Measured as ``visits" by Google Analytics}.

% updates on EOD and the website
Since the documentation described in \cite{Wright2011}, the EOD has expanded its scope: we now do
not require the host star of an exoplanet to be a normal star (e.g.,
exoplanets around pulsars are now included). We now ingest more
parameters describing the exoplanet systems and their host stars, and some
parameters have been revised or deleted. We describe our updates to the
EOD in Section~\ref{sec:update}. The EDE at exoplanets.org has also
expanded its scope and now includes the \kepler\ exoplanet candidates
(KOIs). We describe these changes in Section~\ref{sec:kepler}. The
website exoplanets.org has gone through major back-end changes since
\cite{Wright2011}, which are described in Section~\ref{sec:website}. We
summarize the updates and possible future improvements in
Section~\ref{sec:summary}.

@@

The scope of the EOD has expanded, and there are three major changes
from what was described in \cite{Wright2011}. Previously, we only
included exoplanets orbiting the ``normal stars", but now we are not
limiting the type of host stars (e.g. we included exoplanets orbiting
neutron stars). Furthermore, in \cite{Wright2011}, we only included
exoplanets that were discovered by the RV and transit methods in the
EOD, but now we also include planets discovered via timing (including
pulsar planets and those discovered by eclipse timing). We now include
exoplanets discovered by any other methods with robust detections and
good orbital parameters, such as $\beta$ Pictoris $b$ \citep{Chauvin2012,Nielsen2014,Macintosh2014}.

Previously, we used a generous mass cutoff, recognizing that any
definition of ``exoplanet'' will not necessarily track with the
formation mechanism for an object (which may, after all, be unknown or
unknowable).  Our previous mass cutoff was a minimum mass (m$\sin{i}$)
smaller than 24\mjup; to make this cutoff more relevant to a wide
range of stellar masses and detection methods, we now require the measured
planet-star mass ratio to be smaller than 24 \mjup$/\msun$ ($< 0.023)$.

The rest of the selection criteria for the EOD remain unchanged. We
still require the planets to have robust detections and well-determined
orbits (though these are not strictly quantitative and sometimes subjective; see Section~2 of
\citealt{Wright2011}). If new evidence comes to light and we are no
longer confident about a planet, we may remove it from EOD, even if the
new evidence is not peer reviewed.  The rationale for this scheme is,
as it has been since the CNE, that the EOD represents our best, expert effort to produce a clean set of
trustworthy parameters.  We do not report \textit{all} the announced
exoplanets as we are not trying to provide ``an encyclopedic
presentation of every claimed detection of an 
exoplanet" \citep{Wright2011}.  More comprehensive sets of planet parameters
are available from other exoplanet compendia on the Web.

@@

The DISCMETH field previously reported the method of discovery,
which was either ``radial velocity'' or ``transit''. We have replaced DISCMETH
with {\bf PLANETDISCMETH} and {\bf STARDISCMETH} to better
report how exoplanet systems and individual exoplanets are first
discovered. PLANETDISCMETH reports the discovery method for the
planet, while STARDISCMETH reports the discovery method for the {\it
  planetary system} (i.e. the {\it first}
discovered planet around the host star). These fields are stored
in string format and have one of the following values: ``RV",
``Transit", ``Imaging", ``Microlensing", ``Timing", or ``Astrometry"
(no planets have a value of ``Astrometry" yet since no planet has yet
been {\it discovered} via astrometry).

@@

{\bf KEPID} stands for KEPler ID, which is the integer number assigned
for a Kepler host star. KEPID is only available for unconfirmed
KOI's imported directly from the Exoplanet Archive by the
exoplanets.org backend.

{\bf KOI} stands for Kepler Objects of Interest, which is an object
with transit signals detected by \kepler\ that have not been validated
as being due to exoplanets.  The KOI field defined by the \kepler\
team and shown on the Exoplanet Archive is stored as a floating point
number, consisting of a whole number designated to the host star
followed by a decimal portion denoting a candidate planet. For example,
KOI 102 is a star suspected to host two exoplanets, and KOI 102.01 is
the inner planet candidate and KOI 102.02 is the outer one. Once a
candidate is confirmed, the {\bf NAME} field of the planet is replaced by
the official \kepler\ ID (``Kepler" followed by a hyphen, an integer,
a space, and finally a lower case letter). The KOI number is then used as
{\bf OTHERNAME}. For more information, see
Section~\ref{sec:kepler}.

{\bf EOD} is a Boolean which indicates whether an exoplanet is included
in the EOD for having well-characterized orbital
parameters, such as the orbital period (PER). We added this field because exoplanets.org
now also includes robustly discovered planets that do not have
well-characterized orbits, and also \kepler\ planet candidates (see
Section~\ref{sec:kepler} for more details).  Planets on exoplanets.org
and appearing in the EDE that are not part of the EOD have EOD set to
FALSE (i.e.\ zero).

{\bf MICROLENSING, IMAGING, TIMING} and {\bf ASTROMETRY} are Boolean flags which
indicate that a planet has been detected via these methods. For example,
MICROLENSING $=$ 1 means the planet is detected in a microlensing
event. Note that planets may be detected with multiple methods.

%------------------------------------------------------------------------------
\subsection{Orbital Parameters}\label{sec:orbit}

@@

{\bf MASS} is the mass of the planet in the unit of Jupiter
mass. Previously, we only reported the minimum mass, ($m\sin{i}$,
MSINI) of the planets.  We now, additionally, report the best estimate
of the true mass in a heterogeneous way.  For example, if a planet is discovered by microlensing, we
report the actual mass of the planet according to the literature. If a
planet has both radial velocity and transit measurements, we calculate
the mass from the minimum mass $m\sin{i}$ and the orbital inclination
$i$. For convenience of plotting RV and other planets on a common mass
scale (see Section~\ref{sec:kepler}), MASS is set to MSINI if the
orbital inclination is not known and the reference for MASS ({\bf
  MASSREF}) is set to ``Set to MSINI; I unknown''.

Also for plotting convenience, for transiting $Kepler$ planets without $m\sin{i}$ measured, we estimate their mass using 
mass-radius relations from the literature. We follow a series of
relations given by \footnote{As of the writing of this manuscript,
  Kepler planet candidates on exoplanets.org ingested
  from the Exoplanet Archive have their masses estimated in a slightly
  different manner.  The Website uses the \citeauthor{Mordasini2012} relation for
  planets with 6$\rearth < R < 1 $ \rjup, the \citeauthor{Lissauer2011}
  relation between $1 \rearth < R < 6\rearth$, and $M = (1/R)^{0.306}$ in
  Earth units for planets smaller than $\rearth$.  Updating this
  relation to be consistent with the EOD (and updating the
  corresponding MASSREF fields for these candidates) is a priority
  upgrade for exoplanets.org.}

\[
M_p=
\begin{cases}
M_{\rm WM} &  R<\rearth \\
(1-x)M_{\rm WM} + xM_L  &  \rearth \leq R<4\rearth \\
M_L & 4 \rearth \leq R < 6 \rearth \\
M_M &  6\rearth \leq R < b \\
{\text \mjup} &  R \geq b
\end{cases}
\]

\noindent where $b$ is defined
below, and we use the weight $x=\left(R_{p}/\rearth-1\right)/3$ to
smoothly transition between $M_{\rm WM}$ and $M_L$ in their
overlapping regions of validity. $M_{\rm WM}$ is from \cite{Weiss2014} and is given by 
\[
\frac{M_{\rm WM}}{\mearth}=
\begin{cases}
2.69\left(\frac{R_{p}}{\rearth}\right)^{0.93} &  \rearth \leq R<1.5\rearth \\
0.582\left(0.717+\frac{R_{p}}{\rearth}\right)\left(\frac{R_{p}}{\rearth}\right)^3 &  1.5\rearth\leq R<4\rearth
\end{cases}
\]

$M_L$ is given by $M_{p}/\mearth=\left(R_{p}/\rearth\right)^{2.06}$ from \cite{Lissauer2011}, and $M_M$ is given by 
\[
\log_{10}\left(\frac{M_{p}}{M_0}\right)=-w\left(\frac{b}{\left(R_{p}/\rearth\right)}-1\right)^{1/p}
\]

\noindent from \cite{Mordasini2012}, where
\[
\begin{tabular}{ c c c }
  & $0.1<a/{\rm AU}$ & $0.1<a/{\rm AU} \leq 1$  \\ \hline $M_0[\mearth]$ & 1756.7 & 1308.7 \\
$b[\rearth]$ & 11.684 & 11.858 \\ $w$ & 1.646 & 1.635 \\ $p$ & 2.489 & 2.849 \\ 
\end{tabular}
\]

Planets with masses estimated in this manner are so noted in the
MASSREF field.

{\bf SEP} is a separation between the host star
and the planet in units of AU. For directly imaged and microlensing planets, the
literature usually reports the projected separation and we report the
value accordingly.  If SEP is not directly measured but the semi-major
axis ({\bf A}) is available, then we set SEP to A with its reference,
SEPREF, set to ``Set to A''.

{\bf I} reports the orbital inclination of the planet. Previously, only transiting
systems had $i$ measured, but now some non-transiting systems have
dynamical or astrometric constraints on $i$ (for example, the
microlensing system OGLE-2006-BLG-109L \citep{Bennett2010} and the imaged system, $\beta$ Pictoris \citep{Lagrange2009}).

{\bf BIGOM} is the longitude of the ascending node ($\Omega$) in units
of degrees. At the moment, only $\beta$ Pictoris $b$ has this quantity listed.

{\bf LAMBDA} is the projected spin-orbit misalignment ($\lambda$) in
the plane of the sky in units of degrees. At the moment, $\lambda$
values are only available for the transiting systems, which are
measured by either the Rossiter-McLaughlin effect
\citep[e.g.,][]{Winn2005} or planetary transits of star spots
\citep[e.g.,][]{Sanchis-Ojeda2012}. $\lambda$ is used because
the true spin-orbit angle, defined as the angle between the
stellar spin axis and the orbital axis, is normally not directly
measurable. We follow \cite{Fabrycky2009} who defined the quantity as follows: the
$z$-axis points toward the observer, the $x$-axis points along the
intersection of the sky plane and the planet's orbital plane with the
ascending node of the planet having $x<0$, and the $y$-axis completes
a right handed-triad. $\lambda$ is measured clockwise on the sky from
the $y$-axis to the projected stellar rotational axis. $\lambda$ is
not a newly added field to the EOD but we describe it here because we did not
previously report it consistently, since some literature report the ``projected
spin-orbit misalignment" as $\beta = -\lambda$ instead\footnote{In some cases, \citep[e.g.][]{Moutou2011}, other conventions entirely appear to be used.}. We have sorted
these cases out and made sure that our $\lambda$'s are following the
definition of \cite{Fabrycky2009}.

The {\bf MASSREF} and {\bf MASSURL} fields were used to report the
reference and the URL of stellar mass but now they are used for the planet's
mass; {\bf MSTARREF} and {\bf MSTARURL} are now used for the stellar
mass, {\bf MSTAR}.

@@

We have added two fields since \cite{Wright2011}, which are used for
KOI's incorporated from the Exoplanet Archive.

@@

We have added an entirely new set of fields for secondary
eclipse depths. Previously, due to the limits of instrumentation and limited
sample of exoplanets, there was not much secondary eclipse depth data
available. Since \cite{Wright2011}, as many different surveys have
been launched, secondary eclipse depths at multiple
bands have become available for many planets. Therefore, we added
this entire new set of fields (see Figure~\ref{fig:se}).

@@

The {\bf SE} Boolean indicates whether the system has secondary
eclipse depths measured in any band.  Truth indicates the
system has at least one secondary eclipse measurement in the EOD.

{\bf SET} is the epoch of secondary eclipse center, normally given in BJD but (as with other fields) when the literature reports HJD or UTC JD, we do not attempt a conversion to BJD.

@@

{\bf GAMMA} ($\gamma$) is the radial velocity of the center of mass of
the planetary system with respect to the barycentric frame and is
reported in km/s.  It is typically known to far less precision than
$K$, because it requires an absolute measurement of velocity.

@@

We provide the brightness of the host star measured in different
filters. We report optical magnitude and color ($V$ and $B-V$),
2MASS $J$, $H$, and $K_s$ magnitudes and, we have added {\bf KP} for
the \kepler\ photometric band. Notes that the definitions of $V$ and $B$ in the literature vary, and are often Hipparcos magnitudes.

@@

We report the coordinates of the host star as well as the host star's
ID as designated by different catalogs.  We have added the {\bf DIST} field since
\cite{Wright2011}, which is the distance to the host star in the unit
of pc. If only parallax (PAR) is given, we calculate DIST based on PAR
and vice versa. If the literature does not report DIST or PAR, then we
obtain PAR from the Hipparcos dataset by \cite{van Leeuwen2009} for
stars with Hipparcos numbers. We na\"ively translate the 1-$\sigma$ errors in each into asymmetric
uncertainties in the other.

@@

We have changed the way of reporting uncertainties, especially
asymmetric ones since \cite{Wright2011}. We now report
uncertainties for a certain field X as XUPPER, XLOWER and UX. XUPPER
and XLOWER store the upper and lower 1$\sigma$ uncertainties, and they
are different when the error bars are asymmetric. UX contains the
1$\sigma$ uncertainty, and it equals $({\rm XUPPER+XLOWER})/2$. Fields
that have XUPPER, XLOWER and UX are: all the orbital parameters, all
the transit parameters, all the secondary eclipse fields, and all the stellar
properties and DIST and PAR.

If only an upper limit is given, we set the parameter field X to 0,
the uncertainty XU to half of the upper limit, and the upper error bar
XUPPER to the upper limits (same as XUL). For example, if the
literature reports the upper limit for ECC, which we report in ECCUL,
then we set ECC to be 0, ECCUPPER to ECCUL, and UECC to ECCUL/2.  We
are currently implementing a more precise upper limit scheme (see Section~\ref{sec:summary}.)
